---
title: "Explore Data Types"
output: html_document
---

```{r}
library(stargazer)
MAIN_DIRECTORY <- "~/Kaggle/K06012015"
```

```{r}
setwd(MAIN_DIRECTORY)
meta_data <- read.csv("data/metaData_taxistandsID_name_GPSlocation.csv/metaData_taxistandsID_name_GPSlocation.csv")
head(meta_data)
```
Note: There is a read error on line 41

```{r}
setwd(MAIN_DIRECTORY)
submission_sample <- read.csv("data/sampleSubmission.csv/sampleSubmission.csv")
head(submission_sample)
```
Submission requires a dataset of three variables, (TRIP_ID, LATITUDE, LONGITUDE). These represent a destination.

```{r results='asis'}
setwd(MAIN_DIRECTORY)
test_data <- read.csv("data/test.csv/test.csv")
names(test_data)
```

```{r}
head(test_data[1:8])
```
I believe origin call and origin stand are mutually exclusive. The data should be unique identified by TAXI_ID and TIMESTAMP. The test data doesn't make the submission sample, so we need pull out the destination for cross-validation.

```{r}
#display a single polyline
print(as.character(test_data[1, 9]))
```
Polylines are basically python arrays--this might be easier in python. The pairs are clearly longitude and latitude--reversed in order from the submission sample.

```{r}
setwd(MAIN_DIRECTORY)
train_data <- read.csv("data/train.csv/train.csv", nrows = 50)
head(train_data)
```
Train and test data look similar, good.

We need to get more information on how the the polyline actually relates to the submission data. This should be answered somewhere in the forums.
